Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-17 article_review/Manuscript.tex
changes figures + application

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[!ht]
\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function. There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{Fig1.pdf}
\label{fig:1}       % Give a unique label
\end{figure}

@@

Assume that the number of small first-order indices is known and equals $\gamma$. We denote by $u_1,\dots,u_{\gamma}$ the indices of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$. The cost of Variant $A$ including ``Correlation 2" becomes, 
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^\star},
\label{cost.improvement}
\end{equation}
where: %$m'_{u_j}\leq m^{\star}$, $\ m_{u_j} \leq m^{\star}$, and: 
\begin{itemize}
\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations \\ $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations \\ $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] likewise, for $j\in \mathcal{D}\setminus{\Gamma}$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
\end{itemize}
We recall the cost of Variant $A$ without  ``Correlation 2",
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}. 
%\qquad m_{u_j} \leq m^{\star}.
\label{cost.non.improvement}
\end{equation}
The difference (\ref{cost.improvement}) $-$ (\ref{cost.non.improvement}) equals:
\begin{equation}
 \sum \limits_{j \in \Gamma} 2^{m_{u_j}} \left(2^{m''_{u_j}-m_{u_j}}  + 2^{m'_{u_j}-m_{u_j}} - 1 \right) = \sum \limits_{j \in \Gamma} c_j.
\label{cost.comparison}
\end{equation}
{\color{purple} (Lolo) The sign of \eqref{cost.comparison}} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
\begin{itemize}
\item[1)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations than the first-order index $\underline{S}_{u_j}$. Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
\item[2)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires less evaluations than the first-order index $\underline{S}_{u_j}$. In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.  
\end{itemize}
{\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$. If this assumption holds, we expect to observe case $2)$ more often than case $1)$ and the sign of \eqref{cost.comparison} should be negative or equal to $0$. The validity of this assumption is tested on the numerical examples presented in Section \ref{sec:5}.
%Overall we expect to observe case $2)$ more often than case $1)$. Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$. Hence, it seems reasonable to expect that it will take less points to estimate $\ov{$S$}_u$ than $\underline{S}_u$. 
Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as ``Correlation 2" is shown to perform better for small first-order indices (\textit c.f. \cite{Owen}).}

@@

{\color{purple} (Lolo) To verify the validity of our  assumption saying that the sign of \eqref{cost.comparison} is negative, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}

@@

Table \ref{res.gfunc.Aa} shows the averaged estimation errors obtained with Variant $A.a$ as well as the averaged total number of evaluations performed. Table \ref{res.gfunc.Ab} shows the same results obtained with Variant $A.b$.
\renewcommand{\arraystretch}{1.25}
{\color{purple}(Lolo) (nouvelles tables et figures)
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ & $0.7252$ & $0.0001$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0006$ & $0$ & $0.3481$ & $0.0007$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0007$ & $0$ & $0.0483$ & $0.0005$ & $0$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0025$ & $0.11$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
 $x_5$ & $4.10^{-5}$ & $0.0003$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
 $x_6$ & $4.10^{-5}$ & $0.0003$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $120 \ 638$} & & &\\ \hline 
\end{tabular}
\label{res.gfunc.Aa}
\end{table}
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ & $0.7252$ & $0.0001$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0006$ & $0$ & $0.3481$ & $0.0007$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0013$ & $0$ & $0.0483$ & $0.0005$ & $0$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0003$ & $0$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
 $x_5$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
 $x_6$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $120 \ 832$} & & &\\ \hline 
\end{tabular}
\label{res.gfunc.Ab}
\end{table}}

@@

Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{sobolg_box.eps}
\label{boxplots.gfunc}
\end{figure}

@@

{\color{purple} (Lolo) (REFAIRE BARPLOT MOINS HAUT) 
\begin{figure}[!ht]
\caption{Barplots of the $100$ values taken by the sum of the $c_j$. The distribution is bimodal with $60\%$ values equal to $0$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{sobolg_cj.eps}
\label{cj.gfunc}
\end{figure}
Figure \ref{cj.gfunc} shows barplots of the $100$ values of the sum of the $c_j$. The distribution is bimodal with around $60\%$ of the values equal to $0$ and $40\%$ equal to $512$. As a result, the assumption is validated $60\%$ of the times and Variant A.b does not cost more (or slightly more) than Variant A.a.}
\bigskip

Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. 
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0010$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0018$ & $0.02$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0016$ & $0$    \\ \hline
 $x_5$ & $4.10^{-5}$ & $0.0034$ & $0$  \\ \hline
 $x_6$ & $4.10^{-5}$ & $0.0035$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.gfunc.B}
\end{table}
The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$. However, the total number of evaluations is {\color{purple}half as large}. As such, this approach remains interesting when one wants to estimate only first-order indices.

>>>>

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[!ht]
\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function. There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

@@

Assume that the number of small first-order indices is known and equals $\gamma$. We denote by $u_1,\dots,u_{\gamma}$ the indices of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$. The cost of Variant $A$ including ``Correlation 2" becomes, 
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^\star},
\label{cost.improvement}
\end{equation}
where: %$m'_{u_j}\leq m^{\star}$, $\ m_{u_j} \leq m^{\star}$, and: 
\begin{itemize}
\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations \\ $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations \\ $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] likewise, for $j\in \mathcal{D}\setminus{\Gamma}$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
\end{itemize}
We recall the cost of Variant $A$ without  ``Correlation 2",
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}. 
%\qquad m_{u_j} \leq m^{\star}.
\label{cost.non.improvement}
\end{equation}
The difference (\ref{cost.improvement}) $-$ (\ref{cost.non.improvement}) equals:
\begin{equation}
 \sum \limits_{j \in \Gamma} 2^{m_{u_j}} \left(2^{m''_{u_j}-m_{u_j}}  + 2^{m'_{u_j}-m_{u_j}} - 1 \right) = \sum \limits_{j \in \Gamma} c_j.
\label{cost.comparison}
\end{equation}
{\color{purple} (Lolo) The sign of \eqref{cost.comparison}} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
\begin{itemize}
\item[1)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations than the first-order index $\underline{S}_{u_j}$. Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
\item[2)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires less evaluations than the first-order index $\underline{S}_{u_j}$. In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.  
\end{itemize}
{\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$. If this assumption holds, we expect to observe case $2)$ more often than case $1)$ and \eqref{cost.comparison} verifies the following inequality:
\begin{equation}
\sum \limits_{j \in \Gamma} c_j \leq 0 \ .
\label{assumption}
\end{equation}
The validity of this assumption is tested on the numerical examples presented in Section \ref{sec:5}.
%Overall we expect to observe case $2)$ more often than case $1)$. Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$. Hence, it seems reasonable to expect that it will take less points to estimate $\ov{$S$}_u$ than $\underline{S}_u$. 
Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as ``Correlation 2" is shown to perform better for small first-order indices (\textit c.f. \cite{Owen}).}

@@

{\color{purple} (Lolo) To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}

@@

Table \ref{res.gfunc.Aa} shows the averaged estimation errors obtained with Variant $A.a$ as well as the averaged total number of evaluations performed. Table \ref{res.gfunc.Ab} shows the same results obtained with Variant $A.b$.
\renewcommand{\arraystretch}{1.25}
{\color{purple}(Lolo) (nouvelles tables et figures)
\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ & $0.7252$ & $0.0001$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0006$ & $0$ & $0.3481$ & $0.0007$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0007$ & $0$ & $0.0483$ & $0.0005$ & $0$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0025$ & $0.11$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
 $x_5$ & $4.10^{-5}$ & $0.0003$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
 $x_6$ & $4.10^{-5}$ & $0.0003$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $120 \ 638$} & & &\\ \hline 
\end{tabular}
\label{res.gfunc.Aa}
\end{table}
\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ & $0.7252$ & $0.0001$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0006$ & $0$ & $0.3481$ & $0.0007$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0013$ & $0$ & $0.0483$ & $0.0005$ & $0$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0003$ & $0$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
 $x_5$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
 $x_6$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $120 \ 832$} & & &\\ \hline 
\end{tabular}
\label{res.gfunc.Ab}
\end{table}}

@@

Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
\begin{figure}[t]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{sobolg_box.eps}
\label{boxplots.gfunc}
\end{figure}

@@

{\color{purple} (Lolo)
\begin{figure}[t]
\caption{Barplots of the $100$ values taken by the sum of the $c_j$. The distribution is bimodal with $60\%$ values equal to $0$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.25\textwidth]{sobolg_cj.eps}
\label{cj.gfunc}
\end{figure}
Figure \ref{cj.gfunc} shows barplots of the $100$ values of the sum of the $c_j$. The distribution is bimodal with around $60\%$ of the values equal to $0$ and $40\%$ equal to $512$. As a result, assumption \eqref{assumption} is validated $60\%$ of the times and Variant A.b does not cost more (or slightly more) than Variant A.a.}
\bigskip

\begin{table}[t]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6043$ &  $0.0005$ & $0$ \\ \hline
 $x_2$ & $0.2360$ &  $0.0010$ & $0$ \\ \hline
 $x_3$ & $0.0286$ &  $0.0018$ & $0.02$ \\ \hline
 $x_4$ & $0.0043$ &  $0.0016$ & $0$    \\ \hline
 $x_5$ & $4.10^{-5}$ & $0.0034$ & $0$  \\ \hline
 $x_6$ & $4.10^{-5}$ & $0.0035$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.gfunc.B}
\end{table}
Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$. However, the total number of evaluations is {\color{purple}half as large}. As such, this approach remains interesting when one wants to estimate only first-order indices.
